---
title: "WUP-Linear-Model-with-prediction-2"
author: "Johana Quintanilla"
date: "2025-10-30"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
require(tidyverse)
require(tigerstats)
require(knitr)

data <- read.csv(file="https://onlinestatbook.com/case_studies_rvls/physical_strength/data.txt",sep="",header=TRUE)  
```

### Model1: SIMS-ARM
```{r}
basicNN <- ggplot(data,aes(y=SIMS, x=ARM))
```

```{r}
basicNN + geom_point() + ggtitle("SIMS vs ARM") + theme(plot.title = element_text(hjust = 0.5, size = 20))
```

### Numerical Results

```{r}
cor(SIMS~ARM,data=data)
```

### Inferential Results

```{r}
model.1 <- lm(SIMS~ARM,data=data)
summary.lm(model.1)
```

### Create Target

```{r}
target <- data.frame(ARM=90, GRIP=90)
```

### Predict Target Point of Model 1

```{r}
predict(model.1,target,interval=c("prediction"))
```

### Linear Fit Model1

```{r}
basicNN + geom_point() + ggtitle("SIMS vs ARM") + theme(plot.title = element_text(hjust = 0.5, size = 20)) + geom_smooth(method = lm) 
```

### Model2: SIMS~GRIP
```{r}
basicNN <- ggplot(data,aes(y=SIMS, x=GRIP))
```

```{r}
basicNN + geom_point() + ggtitle("SIMS vs GRIP") + theme(plot.title = element_text(hjust = 0.5, size = 20))
```

### Model2: Numerical Results

```{r}
cor(SIMS~GRIP,data=data)
```

### Model2: Inferential Results

```{r}
model.2 <- lm(SIMS~GRIP,data=data)
summary.lm(model.2)
```

### Predict Target Point of Model 2

```{r}
predict(model.2,target,interval=c("prediction"))
```

### Linear Fit Model2

```{r}
basicNN + geom_point() + ggtitle("SIMS vs GRIP") + theme(plot.title = element_text(hjust = 0.5, size = 20)) + geom_smooth(method = lm) 
```

### Model3: SIMS~ARM+GRIP

### Model3: Numerical Results

```{r}
cor(SIMS~ARM+GRIP,data=data)
```

We noticed that the correlation number in Model 3, SIMS~ARM+GRIP, is higher compared to Model 2 and Model 1. This indicates that the correlation is better when using both models (Model 1 and 2) rather than using them on their own. 

### Model3: Inferential Results

```{r}
model.3 <- lm(SIMS~ARM+GRIP,data=data)
summary.lm(model.3)
```





