---
title: "WUP-Linear-Model-with-prediction-2"
author: "Johana Quintanilla"
date: "2025-10-30"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
require(tidyverse)
require(tigerstats)
require(knitr)

data <- read.csv(file="https://onlinestatbook.com/case_studies_rvls/physical_strength/data.txt",sep="",header=TRUE)  
```

### Model1: SIMS-ARM
```{r}
basicNN <- ggplot(data,aes(y=SIMS, x=ARM))
```

```{r}
basicNN + geom_point() + ggtitle("SIMS vs ARM") + theme(plot.title = element_text(hjust = 0.5, size = 20))
```

### Numerical Results

```{r}
cor(SIMS~ARM,data=data)
```

### Inferential Results

```{r}
model.1 <- lm(SIMS~ARM,data=data)
summary.lm(model.1)
```

### Create Target

```{r}
target <- data.frame(ARM=90, GRIP=90)
```

### Predict Target Point of Model 1

```{r}
predict(model.1,target,interval=c("prediction"))
```

### Linear Fit Model1

```{r}
basicNN + geom_point() + ggtitle("SIMS vs ARM") + theme(plot.title = element_text(hjust = 0.5, size = 20)) + geom_smooth(method = lm) 
```

### Model2: SIMS~GRIP
```{r}
basicNN <- ggplot(data,aes(y=SIMS, x=GRIP))
```

```{r}
basicNN + geom_point() + ggtitle("SIMS vs GRIP") + theme(plot.title = element_text(hjust = 0.5, size = 20))
```

### Model2: Numerical Results

```{r}
cor(SIMS~GRIP,data=data)
```

### Model2: Inferential Results

```{r}
model.2 <- lm(SIMS~GRIP,data=data)
summary.lm(model.2)
```

### Predict Target Point of Model 2

```{r}
predict(model.2,target,interval=c("prediction"))
```

### Linear Fit Model2

```{r}
basicNN + geom_point() + ggtitle("SIMS vs GRIP") + theme(plot.title = element_text(hjust = 0.5, size = 20)) + geom_smooth(method = lm) 
```

### Model3: SIMS~ARM+GRIP

### Model3: Numerical Results

```{r}
cor(SIMS~ARM+GRIP,data=data)
```

We noticed that the correlation number in Model 3, SIMS~ARM+GRIP, is higher compared to Model 2 and Model 1. This indicates that the correlation is better when using both models (Model 1 and 2) rather than using them on their own. 

### Model3: Inferential Results

```{r}
model.3 <- lm(SIMS~ARM+GRIP,data=data)
summary.lm(model.3)
```

The formula for getting Model 3 is -5.433871 + 0.037311*ARM + 0.24470*GRIP. 

### Predict Target Point of Model3

```{r}
predict(model.1,target,interval=c("prediction"))
```

```{r}
predict(model.2,target,interval=c("prediction"))
```

```{r}
predict(model.3,target,interval=c("prediction"))
```

### Anova Test for Models

### Model1~Model3

```{r}
anova(model.1,model.3)
```

Our P-Value was 0.000004994 which is very small. This indicates that model 3 is better than model 1 in a significant difference. 

### Model2~Model3

```{r}
anova(model.2,model.3)
```

Our P-Value for models 2 and 3 is 0.000000001495 which is even smaller than the P-Value of models 1 and 3. This proves that Model 3 is the most accurate model out of the 3 models. 

### Model1~Model2

```{r}
anova(model.1,model.2)
```

The sum of residual sum of square errors of model 2 is greater than model 1. The difference of the two models is -25.189

### Discussion and Conclusion

In this assignment, we learned to import the data from a given website. We were able to manipulate the data into 3 different models. The first model was SIMS~ARM, the second was SIMS~GRIP, and the third was SIMS~ARM+GRIP. We used a prediction code to estimate the values alongside scatter plots to visualize the lines of best fit. We then used Anova to compare all 3 models, and when analyzing in the end, it showed us that model 3 has the best accuracy out of all 3 models. 







